Pipeline Performance Figure Generation

### 2023-06-29 TestingPipeline/Scripts/paper_figure_generation.Rmd
Some updates to flowchart.

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = c(rep(viridis(3)[1], 5), rep(viridis(3)[2], 4), viridis(3)[3]),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common_3_breaks.png",
                  annotation_legend = T)
```

@@

>>>>

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = c(rep(viridis(3)[1], 5), rep(viridis(3)[2], 4), viridis(3)[3]),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common_3_breaks.png",
                  annotation_legend = T)

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = c(viridis(4)[1], rep(viridis(4)[2], 4), rep(viridis(4)[3], 4), viridis(4)[4]),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common_4_breaks.png",
                  annotation_legend = T)

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = viridis(5),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common_5_breaks.png",
                  annotation_legend = T)
```

@@

```{r}
viruses_from_tv <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = F,
                                              include_virsorter2 = F,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = F,
                                              include_virsorter = F)

table(viruses_from_tv, viruses$seqtype)
```

```{r}
viruses_from_ntv <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = F,
                                              include_virsorter2 = F,
                                              include_tuning_viral = F,
                                              include_tuning_not_viral = T,
                                              include_virsorter = F)

table(viruses_from_ntv, viruses$seqtype)
```
